\Title

### 2021-07-01 manuscript/content.tex
Revise the australia results

This section will demonstrate how gradient-boosted equivalent sources can be
used to interpolate large datasets of gravity data onto a regular grid at
uniform height.
For this purpose, we selected an open-access compilation of ground gravity
surveys over Australia made by \citet{wynne2018} and filtered and referenced to
the WGS84 ellipsoid by \citet{australia_compilation}.
It contains over 1.7 million data points and covers most of the Australian
territory at variable point spacings.
Our goal is to create a 1~arc-minute resolution grid of gravity disturbances at
a constant geometric height of \AustraliaEqlGridHeight{} (the largest height of
observations).

@@

We start the interpolation process by defining a set of block-averaged sources
using a block size of 1.8\km{}, resulting in a total of
\AustraliaEqlNSources{}~point sources which depths remain unknown for now.
The block size was chosen to match the desired resolution of the final grid
 (1~arc-minute is approximately 1.8\km{} at the equator).
Then we need to determine the size of the windows that will be used for
estimating the coefficients of the gradient-boosted equivalent sources.
We computed the amount of computer memory needed in order to store the largest
Jacobian matrix for different values of window size
(Fig.~\ref{fig:australia-memory-cv-error}a).
We have chosen a window size of \AustraliaEqlWindowSize{} in order to limit the
amount of memory needed to under 16~Gigabytes.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-memory-cv-error.pdf}
    \caption{
        (a) Amount of computer memory needed to store the largest Jacobian
        matrix vs different window sizes. Each memory requirement corresponds
        to the ammount of memory needed to store the elements of the largest
        Jacobian matrix during the process of estimating the gradient-boosted
        equivalent sources coefficients, using a double precision floating
        point for each (64 bits).
        (b) Root-mean square errors obtained after the K-Fold cross-validation
        for each pair of damping and depth parameters. The orange
        square highlights the minimum RMS value.
        (c) Root-mean square error of the residuals after each iteration of the
        coefficients estimation process.
    }
    \label{fig:australia-memory-cv-error}
\end{figure*}

Secondly, we need to determine the depth of the sources and the value for the
damping parameter. Based on the results obtained in
Section~\ref{sec:synthetic_distributions}, we have chosen to locate them using
the \emph{relative depth} strategy.
In order to determine the values for the \emph{depth} and \emph{damping}
parameters, we have applied a K-Fold cross-validation method through the
scikit-learn implementation \citep{sklearn2011}.
It consists in randomly dividing the original data into $k$ small sets (or
folds), estimate the source coefficients using only $k - 1$ of the folds
(training data) and validate the model by comparing its predictions with the
remaining fold (testing data). This process is carried out once for each one of
the $k$ folds.
With the goal of speeding up the computations, we selected a portion of the
Australia gravity disturbances to run the cross-validation: an area of
\AustraliaSmallAreaEastingSize{}$\times$\AustraliaSmallAreaNorthingSize{}
containing \AustraliaSmallAreaNPoints{} points.
We run the cross-validation with a combination of \emph{depth} ranging from
\AustraliaDepthMin{} to \AustraliaDepthMax{},
and \emph{damping} from
\AustraliaDampingMin{} to \AustraliaDampingMax{} in steps of one order of
magnitude.
We have used the root-mean square error as the validation function between the
testing data and the predictions on each k-fold and computed the mean of all
the RMS for each combination of the \emph{depth} and \emph{damping} parameters.
Figure \ref{fig:australia-memory-cv-error}b shows the resulting scores of the
cross-validation and highlights the minimum value achieved:
\AustraliaEqlRmsScore{} corresponding to a relative depth of \AustraliaEqlDepth{} and
a damping equal to \AustraliaEqlDamping{}.

Finally, we proceed to estimate the coefficients of the whole set of
gradient-boosted equivalent sources using the parameters previously determined.
Fig.~\ref{fig:australia-memory-cv-error}c shows the root-mean square of the
residuals after each iteration of the gradient-boosting algorithm, exposing how
the algorithm converges at a minimum difference between the gravity disturbance
data and the predicted values by the equivalent sources.
We then used the estimated source coefficients to predict the values of the
gravity disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid.
Fig.~\ref{fig:australia} shows the original data distribution and the
interpolated regular grid.
Grid points that are further than 50\km{} from the nearest data
point are masked to avoid unrealistic extrapolations.

Fig.~\ref{fig:australia-residuals} shows the residuals on each observation
point: the difference between the gravity disturbance data and the predicted
values by the equivalent sources on the same points.
The inset figure shows a histogram of the residual values, depicting that the
residuals are normally distributed around zero.

@@

>>>>

This section will demonstrate how gradient-boosted equivalent sources can be
used to interpolate large datasets onto regular grids at uniform height.
For this purpose, we selected an open-access compilation of ground gravity
surveys over Australia made by \citet{wynne2018} and filtered and referenced to
the WGS84 ellipsoid by \citet{australia_compilation}.
It contains over 1.7 million data points and covers most of the Australian
territory at variable point spacings.
Our goal is to create a 1~arc-minute resolution grid of gravity disturbances at
a constant geometric height of \AustraliaEqlGridHeight{} (the largest height of
observations).

@@

We start the interpolation process by defining a set of block-averaged sources
using a block size of 1.8\km{}, resulting in a total of
\AustraliaEqlNSources{}~point sources.
The block size was chosen to match the desired resolution of the final grid
(1~arc-minute is approximately 1.8\km{} at the equator).
Based on the results obtained in Section~\ref{sec:synthetic_distributions}, we
have chosen to use the \emph{relative depth} strategy.
The window overlap was once again fixed at 50\%.
To determine the size of the windows, we computed the amount of computer memory
needed to store the largest Jacobian matrix for different values of window size
(Fig.~\ref{fig:australia-memory-cv-error}a).
We have chosen a size of \AustraliaEqlWindowSize{} in order to limit the
amount of memory needed to under 16~Gigabytes.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-memory-cv-error.pdf}
    \caption{
        (a) Amount of computer memory needed to store the largest Jacobian
        matrix for different window sizes. Our implementation uses double
        precision floating point numbers (64 bits) for the Jacobian.
        (b) K-Fold cross-validation root-mean square errors obtained after the
        for each pair of damping and depth parameters. The orange
        square highlights the minimum.
        (c) Root-mean square error against the observed data after each
        iteration of the gradient-boosting algorithm.
    }
    \label{fig:australia-memory-cv-error}
\end{figure*}

We determined the depth of the sources and the damping parameter by applying
K-Fold cross-validation through the scikit-learn library \citep{sklearn2011}.
The method randomly divides the original data into $k$ sets (folds), fits the
model using only data from $k - 1$ folds, and validates the model by comparing
its predictions against the one remaining fold.
This process is carried out once for each one of the $k$ folds, leading to
an estimated mean cross-validation RMS error for the model.
To speed up the computation, we only performed the cross-validation on a subset
of the data corresponding to an area of
\AustraliaSmallAreaEastingSize{}$\times$\AustraliaSmallAreaNorthingSize{}
containing \AustraliaSmallAreaNPoints{} points.
We ran the cross-validation repeatedly for combinations of \emph{depth},
ranging from \AustraliaDepthMin{} to \AustraliaDepthMax{},
and \emph{damping}, from \AustraliaDampingMin{} to \AustraliaDampingMax{} in
steps of one order of magnitude.
Figure \ref{fig:australia-memory-cv-error}b shows the resulting
cross-validation RMS errors and highlights the minimum value of
\AustraliaEqlRmsScore{}, which corresponds to a relative depth of
\AustraliaEqlDepth{} and a damping equal to \AustraliaEqlDamping{}.

Finally, we proceeded to estimate the source coefficients using the entire
dataset and the parameters previously determined.
Fig.~\ref{fig:australia-memory-cv-error}c shows the RMS error against the
observed data after each iteration of the algorithm.
The estimated source coefficients were then used to predict the values of the
gravity disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid.
Fig.~\ref{fig:australia} shows the original data distribution and the
interpolated grid.
Grid points that are further than 50\km{} from the nearest data point are
masked to avoid unrealistic extrapolations.

@@

Fig.~\ref{fig:australia-residuals} shows the difference between the observed
and predicted gravity disturbances.
The inset figure shows a histogram of these residuals, which are approximately
normally distributed around zero.
The largest residuals are located in regions with high-amplitude
short-wavelength features in the observed data.
